%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Computer Vision Intern, CVisionAI} % Job title
    {Inspektlabs} % Organization
    {Dwarka, Delhi} % Location
    {Nov 2019 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {It is startup which help their customer in easy claim assessment using Machine Learning and deep learning. It is Started by IIT-Delhi and ISB alumni. It is now a part of barclays-london-program. }
        \item {Built Object detection model like R-FCN, Cascade RCNN, EfficientDet-D6, CornerNet. My work was to do many experiments on these models and improve mAP on our 25k dataset (Damage Detection).}
        \item {Studied research papers to find model behaviour and tuned the hyper parameter accordingly.}
         \item {developed many utility scripts which helped in day to day work.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Vice Chairperson} % Job title
    {IEEE-MAIT} % Organization
    {Delhi} % Location
    { Jan 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {I was promoted to vice chair after being Technical coordinator of IEEE-MAIT for a year.}
        \item {Handle all day to day job of our society.}
        \item {Teaching a weekly class on Machine Learning in our college.}
        \item {Mentor of Ethical Hacking, PCB designing and Machine Learning Workshop.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
     % Job title
    {Technical Intern}
    {LBD Pvt.Ltd}% Organization
    {Delhi} % Location
    {Apr 2018 - Jul 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item { LBD Robotics is Start-up by Mr. Mayank Gupta, former DTU Professor.}
        \item { They work in area of Robotics, R.O.S, Electronics and Embedded system. My day to day work was PCB designing, Learning Python and understanding client Handling.I completed making Arduino from scratch on Professional software called Altium.}
        \item {Learned Python and performed many Experiments.}
        %  \item { Helped students refine their work that actively improves Terasology}
      \end{cvitems}
    }
%---------------------------------------------------------
 % \cventry
    % {Managment Intern} % Job title
    % {Umeed NGO} % Organization
    % {Delhi} % Location
    % {Jun 2018 - Aug 2018} % Date(s)
    % {
    %   \begin{cvitems} % Description(s) of tasks/responsibilities
    %     \item{Teached students in slum area and did a survey.}
    %     \item {Part of a awareness campaign to save water in CP,Delhi}
    %     \item {Managed to bring volunteers, donations to the NGO}
    %   \end{cvitems}
    % }

\end{cventries}
